Kimbee: A Speech Therapy Application For Children

### 2015-03-08 Paper/paper.tex

\documentclass{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}

\usetikzlibrary{automata,positioning}

\topmargin=-0.30in
\evensidemargin=0in
\oddsidemargin=0.25in
\textwidth=6in
\textheight=8.80in
\headsep=0.25in

\linespread{1.1}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\renewcommand*\contentsname{Table of Contents}

@@

\vspace{0.65 in}
\begin{centering}
\LARGE{\textbf{Kimbee: A Speech Therapy \\Application For Children}}\\[7 pt]
\Large{Ryan Drapeau \hspace{30 pt} Nick Huynh \hspace{30 pt} Aaron Nech}\\[5 pt]
\large{\{drapeau, necha, huynick\}@cs.washington.edu}

\end{centering}

\vspace*{1.25 in}

\begin{centering}
\section*{Abstract}

\end{centering}

[ABSTRACT HERE]

\newpage

@@

% CONTENT

@@

>>>>

% \documentclass{acm_proc_article-sp}
\documentclass{sig-alternate-2013}

@@

\title{Kimbee: A Speech Therapy Application For Children}

\numberofauthors{1}
\author{
    \alignauthor
    \vspace*{-0.3in}
        Ryan Drapeau \hspace{3.0cm}
        Nick Huynh \hspace{3.0cm}
        Aaron Nech \\
    \affaddr{
        \hspace{0.3cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{1.4cm}
        University of Washington \hspace{0cm}
        } \\[7 pt]
    \email{{\centering \{drapeau, huynick, necha\}@cs.washington.edu}}
}

\maketitle

\begin{abstract}

Many kids have difficulty pronouncing certain sounds and their parents are forced to pay for speech therapy for their children. We hope to create a web application that doubles as a game in order to help children who are undergoing speech therapy recognize and pronounce certain sounds. The game should keep children wanting to play more, making their speech therapy seem like less of a chore and help them learn by having the children try say the word then correct or reward them depending on their pronunciation. We will speak with a professional speech therapist in order to help shape our game and the feedback it gives back to children in order to give more constructive feedback than simply repeating the correct pronunciation back to them.

\end{abstract}

% \cite{Lamport:LaTeX}

@@

@@

\section{Acknowledgments}

\bibliographystyle{abbrv}
\bibliography{sigproc}

\balancecolumns
